We are not the 99 percent: quantifying asphericity in the distribution of Local Group satellites

### 2017-11-04 paper/paper.tex
conclusions

In this paper we develop and demostrate a method to quantify the
asphericity of the satellite distribution in the Local Group.
The method uses as a basic condition the spherical randomization of
satellite positions (observed or simulated). 
The scalars describing the satellite distribution in each galaxy are
then normalized to the mean value and standard deviation in the
randomized samples.

In observations we limit our analysis to the 11 brightest satellites 
in the Milky Way and Andromeda. 
For numerical data we use the Illustris-1 and the ELVIS simulations.

@@

>>>>

In this paper we develop and demostrate a method to quantify the
asphericity of the satellite distribution in the Local Group.
The method uses as a basic condition the spherical randomization of
satellite positions (observed or simulated). 
The scalars describing the satellite distribution in each galaxy are
then normalized to the mean value and standard deviation in the
randomized samples. 
In observations we limit our analysis to the 11 brightest satellites 
in the Milky Way and Andromeda. 
For numerical data we use the Illustris-1 and the ELVIS simulations.

@@

The method we present to quantify how atypical is the LG is robust to
the numerical simulations used to define the LCDM expectations. 
Quantifying the degree of asphericity highlights the atypicality of
the Milky Way stressing the stark difference with M31 and its more
typical nature. 
This atypical distribution also adds up to the presence of two bright
satellite galaxies, which is also uncommon both in simulations and
observations.

The extension of the framework we present in this paper to describe
outliers found as a second order deviation (i.e. fiding a \emph{subset} of
satellites in M31 that are in a plane or \emph{adding} velocity
information) could also be possible along the line of work presented
by, that avoid finding in observations the exact observed distribution
and instead focuse in defining atypicallity.

The quantitative study we present allows us to estimate  the volumes 
that cosmological simulations have to probe in order to study similar
LG configurations.
Such atypical satellite distribution should be seen as an opportunity
to constraint in high detail the initial conditions and environment
that allowed such pattern to emerge.
